Collapse Weddell and Check consistency

### 2023-09-28 WeddellSea_collapse.Rmd
Updated ms

@@

search_value <- "Dictyocha"
result <- classall_df %>% filter(if_any(kingdom:suborder, ~grepl(search_value, .,ignore.case=TRUE)))
```

>>>>

require(NetIndices)
a <- get.adjacency(gM,sparse=F)
tl <- TrophInd(a)
tl[rownames(tl)==search_value,]

@@

search_value <- "Foraminifera"
result <- classall_df %>% filter(if_any(kingdom:suborder, ~grepl(search_value, .,ignore.case=TRUE)))
dtot1 <- replace_nodes(dtot, result, "phylum")
collapsed_w <- dtot1 %>% distinct()
gM <- graph_from_edgelist(as.matrix(collapsed_w), directed  = T)
degree(gM)[search_value]

a <- get.adjacency(gM,sparse=F)
tl <- TrophInd(a)
tl[rownames(tl)==search_value,]

search_value <- "Dictyocha" # Sillicoflagelados
result <- classall_df %>% filter(if_any(kingdom:suborder, ~grepl(search_value, .,ignore.case=TRUE)))
degree(gM)[result$Taxon]
tl[rownames(tl)==result$Taxon,]

search_value <- "Silico" # Sillicoflagelados
result <- classall_df %>% filter(if_any(kingdom:suborder, ~grepl(search_value, .,ignore.case=TRUE)))
degree(gM)[result$Taxon]

search_value <- "Cryptophy" # Cryptophyta -------------> NO HAY
result <- classall_df %>% filter(if_any(kingdom:suborder, ~grepl(search_value, .,ignore.case=TRUE)))
```
